### 2014-06-12 src/paper1/discussion.tex
Fixed some references

\section{Appendix}

@@

% Equation 13
\begin{equation}
\label{p1eqn13}
\tilde{H}_S = w_{HS} \cdot \hat{H}_S + w_{HP} \cdot H_{SP},
\end{equation}

@@

% Equation 14
\begin{equation}
\label{p1eqn14}
w_{HS} = \frac{1 / \sigma^2_{HS}}{1 / \sigma^2_{HS} + 1 / \sigma^2_{HSP}},
\end{equation}

@@

% Equation 15
\begin{equation}
\label{p1eqn15}
w_{HP} = \frac{1 / \sigma^2_{HSP}}{1 / \sigma^2_{HS} + 1 / \sigma^2_{HSP}},
\end{equation}

in which sHS denotes the noise in the sensory signal, known to the observer, and wHS and wHP represent the relative weights of the sensory signal and the prior, respectively. Note that Equation 13 is equivalent to Equation 1 in Materials and Methods. The variance of the posterior distribution in a single trial is given by the following:

% Equation 16
\begin{equation}
\label{p1eqn16}
\sigma^2_{HS} = w_{HS} \cdot \sigma^2_{HS} \\
              = \frac{\sigma^2_{HSP}}{\sigma^2_{HS} + \sigma^2_{HSP}} \cdot \sigma^2_{HS}
\end{equation}

@@

That the variance of the peak locations across multiple trials, $\sigma^2(\tilde{H}_S)$, is smaller can be shown by applying the rules of noise propagation to Equation 13.

@@

which is equivalent to Equation 10 in Materials and Methods. Corresponding panels G-I (Fig. 8) illustrate the distribution of the sensory signals for a given tilt angle (green-shaded curve), the prior distribution (blue-shaded curve), and the optimal estimates (orange-shaded curve), respectively. Figure 8I illustrates that the distribution of the optimal estimates across many trials has a lower variance than the posterior distribution in each single trial (Fig. 8B), which follows from the comparison of Equations 16 and 17, respectively.

>>>>

\section{Appendix}
\label{p1:sec:appendix}

@@

% Equation 13
\begin{equation}
\label{p1:eqn13}
\tilde{H}_S = w_{HS} \cdot \hat{H}_S + w_{HP} \cdot H_{SP},
\end{equation}

@@

% Equation 14
\begin{equation}
\label{p1:eqn14}
w_{HS} = \frac{1 / \sigma^2_{HS}}{1 / \sigma^2_{HS} + 1 / \sigma^2_{HSP}},
\end{equation}

@@

% Equation 15
\begin{equation}
\label{p1:eqn15}
w_{HP} = \frac{1 / \sigma^2_{HSP}}{1 / \sigma^2_{HS} + 1 / \sigma^2_{HSP}},
\end{equation}

in which sHS denotes the noise in the sensory signal, known to the observer, and $w_{HS}$ and $w_{HP}$ represent the relative weights of the sensory signal and the prior, respectively. Note that Equation \ref{p1:eqn13} is equivalent to Equation \ref{p1:eqn1} in \nameref{p1:sec:methods}. The variance of the posterior distribution in a single trial is given by the following:

% Equation 16
\begin{equation}
\label{p1:eqn16}
\sigma^2_{HS} = w_{HS} \cdot \sigma^2_{HS} \\
              = \frac{\sigma^2_{HSP}}{\sigma^2_{HS} + \sigma^2_{HSP}} \cdot \sigma^2_{HS}
\end{equation}

@@

That the variance of the peak locations across multiple trials, $\sigma^2(\tilde{H}_S)$, is smaller can be shown by applying the rules of noise propagation to Equation \ref{p1:eqn13}.

@@

which is equivalent to Equation \ref{p1:eqn10} in Materials and Methods. Corresponding panels G-I (Fig. \ref{p1:fig8}) illustrate the distribution of the sensory signals for a given tilt angle (green-shaded curve), the prior distribution (blue-shaded curve), and the optimal estimates (orange-shaded curve), respectively. Figure 8I illustrates that the distribution of the optimal estimates across many trials has a lower variance than the posterior distribution in each single trial (Fig. 8B), which follows from the comparison of Equations 16 and 17, respectively.

### 2014-06-12 src/paper1/intro.tex
Fixed some references

Instead, we took optimality as a starting point and implemented an inverse probabilistic approach to deduce noise levels of the various individual sensors. We probed two spatial orientation estimates---body-in-space and head-in-space orientation--- which, according to optimal theory, will use all available sensory signals that can be obtained by various reference frame transformations. This transformation and integration scheme, shown in Figure 1, involves at least three sensory systems: (1) head sensors, supplying information about the orientation of the head with respect to gravity (vestibular system); (2) body sensors, providing an estimate of the orientation of the body in space (``somatic graviceptors'') \cite{mittelstaedt1997}; and (3) neck sensors, providing an estimate of the angle between head and body (neck proprioceptors).

@@

    \caption{Schematic representation of the sensory integration model. Sensory signals, denoted by a hat symbol ($\hat{ }$), are assumed to be calibrated accurately, but contaminated by Gaussian noise. Optimal estimates are denoted by a tilde ($\tilde{ }$). Body sensors, neck sensors, and otoliths provide information about orientation of body in space ($B_S$), head on body ($H_B$), and head in space ($H_S$), respectively. Neck signal ($\hat{H}_B$) is used for a reference frame transformation of otolith information into a body-in-space signal ($\hat{H}_S - \hat{H}_B = \hat{B}_{SI}$), and for a transformation of body-tilt information into a head-in-space signal ($\hat{B}_S + \hat{H}_B = \hat{H}_{SI}$). For an optimal estimate of body-in-space orientation, $\tilde{B}_S$ (SBT task), the model combines the body-sensor signal ($\hat{B}_S$, red pathway) with a reference-frame-transformed otolith signal ($\hat{B}_{SI}$, green pathway). Relative contributions of the two pathways ($w_{BD}$ and $w_{BI}$) depend on their relative precision (Eq. \ref{p1eqn2}). The scheme shows a symmetrical arrangement with two priors, but there is ample reason to believe that their effects are not identical. The simplest explanation of current and previous SBT data (see \nameref{sec:mm}, \nameref{sec:mm:da:sbt}) indicates that the associated prior in this task is uniform, which implies that $w_{BP}$ can be ignored. In the SVV task, an optimal estimate of head-in-space ($\tilde{H}_S$) is obtained by integration of otolith information ($\hat{H}_S$, green pathway), reference-frame-transformed information from body sensors ($\hat{H}_{SI}$, red pathway), and a significant contribution from prior information ($H_{SP}$, blue pathway). Relative weights are denoted by $w_{HD}$, $w_{HI}$, and $w_{HP}$, respectively. Estimate of line-in-space orientation is obtained by combining $\tilde{H}_S$ and estimates of eye-in-head ($\tilde{E}_H$) and line-on-eye ($\tilde{L}_E$) orientation. Noise variance in body sensors ($\sigma^2_{BS}$), neck sensors ($\sigma^2_{HB}$), otoliths ($\sigma^2_{HS}$), and width of prior ($\sigma^2_{HSP}$) defines their relative weights (see Materials and Methods). Otolith noise may depend on tilt angle (Eq. \ref{p1eqn11}). Note that the process of sensory integration, denoted here by summation of weighted sensory signals, is equivalent to multiplication of the underlying probability distributions (Eqs. \ref{p1eqn2} and \ref{p1eqn6} and Appendix).}
\end{figure}

>>>>

Instead, we took optimality as a starting point and implemented an inverse probabilistic approach to deduce noise levels of the various individual sensors. We probed two spatial orientation estimates---body-in-space and head-in-space orientation--- which, according to optimal theory, will use all available sensory signals that can be obtained by various reference frame transformations. This transformation and integration scheme, shown in Figure \ref{p1:fig1}, involves at least three sensory systems: (1) head sensors, supplying information about the orientation of the head with respect to gravity (vestibular system); (2) body sensors, providing an estimate of the orientation of the body in space (``somatic graviceptors'') \cite{mittelstaedt1997}; and (3) neck sensors, providing an estimate of the angle between head and body (neck proprioceptors).

@@

    \caption{Schematic representation of the sensory integration model. Sensory signals, denoted by a hat symbol (\textasciicircum), are assumed to be calibrated accurately, but contaminated by Gaussian noise. Optimal estimates are denoted by a tilde (\textasciitilde). Body sensors, neck sensors, and otoliths provide information about orientation of body in space ($B_S$), head on body ($H_B$), and head in space ($H_S$), respectively. Neck signal ($\hat{H}_B$) is used for a reference frame transformation of otolith information into a body-in-space signal ($\hat{H}_S - \hat{H}_B = \hat{B}_{SI}$), and for a transformation of body-tilt information into a head-in-space signal ($\hat{B}_S + \hat{H}_B = \hat{H}_{SI}$). For an optimal estimate of body-in-space orientation, $\tilde{B}_S$ (SBT task), the model combines the body-sensor signal ($\hat{B}_S$, red pathway) with a reference-frame-transformed otolith signal ($\hat{B}_{SI}$, green pathway). Relative contributions of the two pathways ($w_{BD}$ and $w_{BI}$) depend on their relative precision (Eq. \ref{p1eqn2}). The scheme shows a symmetrical arrangement with two priors, but there is ample reason to believe that their effects are not identical. The simplest explanation of current and previous SBT data (see \nameref{p1:sec:methods}, \nameref{p1:sec:sbt_computation}) indicates that the associated prior in this task is uniform, which implies that $w_{BP}$ can be ignored. In the SVV task, an optimal estimate of head-in-space ($\tilde{H}_S$) is obtained by integration of otolith information ($\hat{H}_S$, green pathway), reference-frame-transformed information from body sensors ($\hat{H}_{SI}$, red pathway), and a significant contribution from prior information ($H_{SP}$, blue pathway). Relative weights are denoted by $w_{HD}$, $w_{HI}$, and $w_{HP}$, respectively. Estimate of line-in-space orientation is obtained by combining $\tilde{H}_S$ and estimates of eye-in-head ($\tilde{E}_H$) and line-on-eye ($\tilde{L}_E$) orientation. Noise variance in body sensors ($\sigma^2_{BS}$), neck sensors ($\sigma^2_{HB}$), otoliths ($\sigma^2_{HS}$), and width of prior ($\sigma^2_{HSP}$) defines their relative weights (see \nameref{p1:sec:methods}). Otolith noise may depend on tilt angle (Eq. \ref{p1:eqn11}). Note that the process of sensory integration, denoted here by summation of weighted sensory signals, is equivalent to multiplication of the underlying probability distributions (Eqs. \ref{p1:eqn2} and \ref{p1:eqn6} and \nameref{p1:sec:appendix}).}
    \label{p1:fig1}
\end{figure}
